% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
%\usepackage{natbib}
\usepackage{filecontents}
\usepackage{cite} % uses cite package for formatting the publications
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\topmargin = -.5in
\setlength{\textheight}{10in} 

\def\FormatName#1{%
  \def\myname{Herron}%
  \edef\name{#1}%
  \ifx\name\myname
    \textbf{#1}%
  \else
    #1%
  \fi
}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\name{\Huge{Casey Herron}}
\address{801 17th Ave\\Seattle, WA 98122} 
\address{\textit{T:} (734) 754-6020\\\textit{Email:} casey.m.herron@gmail.com}
\begin{resume}

\section{EXPERIENCE}
\vspace*{+0.2cm}
\textbf{Data and Applied Scientist II}, \textit{Microsoft} \hfill \textbf{2015 - Present}
%Redmond, Washington
\begin{itemize} \itemsep -2pt
\item Easing transition from AWS to Azure
\item SPARK integration, HDInsight, Azure Data Lake, WebHDFS
\item Continuation of the Revolution job transitioning to Microsoft
\end{itemize}

\textbf{Data Scientist}, \textit{Revolution Analytics} \hfill \textbf{2013 - 2015}
%Seattle, Washington
\begin{itemize} \itemsep -2pt
\item Wearing many hats within the RevoScaleR development team
\item Designated Scrum Master
\item Analytics tackled: Naive Bayes, Tree/Forest Algorithms, Linear and Logistic Regression, Chunking algorithms,
\item Hadoop and other distributed platforms 
\end{itemize}

\textbf{Statistical Research Associate}, \textit{Fred Hutchinson Cancer Research Center} \hfill \textbf{2011 - 2013}%\\
%\textit{Statistical Center for HIV/AIDS Research and Prevention}
%Seattle, Washington\\
\begin{itemize} \itemsep -2pt
\item Lead statistical support for study design, data collection, and data analysis for three HIV prevention clinical trials
\item Statistical programming in R and SAS
\item Developed strong written and verbal communication skills including ability to tailor content and delivery of results to a diverse audience regardless of their of statisical acumen
\item Analysis efforts resulted in three publications and one abstract/poster at the 2011 Society for Clinical Trials meeting
\end{itemize}

\textbf{University of Michigan}, Ann Arbor, Michigan\\
\textit{Graduate Student Instructor, Department of Statistics} \hfill \textbf{2011}
\begin{itemize} \itemsep -2pt
\item Taught an undergraduate course, Introduction to Statistics and Data Analysis
\end{itemize}
\textit{Graduate Student Research Assistant, Department of Biostatistics} \hfill \textbf{2010}
\begin{itemize} \itemsep -2pt
\item Genetics Rotation: Developed analysis in R identifying regions of chromosomal loss associated with clinical outcomes in tumor samples from patients with Lung Cancer.
\item Clinical Trials Rotation: Analyzed data from a clinical trial looking at the efficacy of an incontinence intervention in women with pelvic floor disorder in SAS.  
\end{itemize}

\textbf{University of Michigan, Department of Human Genetics}, Ann Arbor, Michigan\\
\textit{Laboratory Specialist Intermediate} \hfill \textbf{2007 - 2009}
\begin{itemize} \itemsep -2pt
\item Successfully extracted DNA from many types of human tissues
\item Developed and implemented protocols for sequencing DNA to look for germline mutations in families from the University of Michigan Cancer Genetics Clinic
\item Entered data into an Oracle database and used SQL queries within SAS to summarize data for lab meetings and publications
\item Contributions resulted in four publications
\end{itemize}

\section{EDUCATION}
\vspace*{+0.2cm}
\textbf{University of Michigan}, Ann Arbor, Michigan\\
\begin{tabular}{ p{10cm} l } 
M.S., {Biostatistics}, 2011\\
%Relevant Coursework: Categorical Data Analysis, Generalized Linear Models, Non-Parametric Methods, and Survival Analysis\\
%Adviser: Dr. Jeremy Taylor
\end{tabular}

%\textbf{Washtenaw Community College}, Ypsilanti, Michigan\\
%\begin{tabular}{ p{10cm} l }
%Introduction to Programming with C++, Spring 2009
%\end{tabular}

\textbf{Kalamazoo College}, Kalamazoo, Michigan\\
\begin{tabular}{ p{10cm} l }
B.A., {Mathematics}, 2007\\
Semester Abroad, \textit{University of Aberdeen, Aberdeen, UK}
%Adviser: Dr. Eric Barth\\
%Relevant Coursework: Scientific Computing (MATLAB and C), Linear Algebra, Statistical Theory, and Probability (R)\\
\end{tabular}

%\textbf{University of Aberdeen}, Aberdeen, United Kingdom\\
%\begin{tabular}{ p{10cm} l }
%Semester Abroad, Fall 2005
%\end{tabular}

\section{TECHNICAL SKILLS} 
Languages: R, SAS, SQL\\
Databases: MySQL, Oracle, MS SQL Server, HSQL, PostgreSQL\\
Platforms: *NIX, Mac, Windows
Distributed Platforms: Hadoop, Linux LSF, Teradata, and MS SQL Server
Web Applications: Amazon Web Services, Microsoft Azure, Jenkins, JIRA
Misc: Subversion, git, ansible, bash scripting 

\renewcommand\refname{}
\section{Peer Reviewed Publications}
%\vspace*{-0.25cm}
\renewcommand{\section}[2]{}%
\begin{filecontents}{herroncm.bib}
@article{casey7,
author = {{Fowler}, M.~G. and {Coovadia}, J. and {Herron}, C.~M. and {Maldonado}, Y. and {Chipato}, T. and {Moodley}, D. and {Musoke}, P. and {Aizire}, J. and {Manji}, K. and {Stanix-Chibanda}, L. and {Fawzi}, W. and {Chetty}, V. and {Msweli}, L. and {Kisenge}, R. and {Brown}, E.~R. and {Mwatha}, A. and {Eshelman}, S.~H. and {Richardson}, P. and {Allen}, M. and {George}, K. and {Andrew}, P. and {Zwerski}, S. and {Mofenson}, L.~M. and {Jackson}, J.~B.},
title = "{Efficacy and safety of an extended nevirapine regimen in infants of breastfeeding mothers with HIV-1 infection for prevention of HIV-1 transmission (HPTN 046): 18-month results of a randomized, double-blind, placebo-controlled trial.}",
journal = {J. Acquir. Immune. Defic. Syndr.},
year = 2014,
volume = 65,
pages = {366-374},
}

@article{casey6,
author = {{Mirochnick}, M. and {Taha}, T. and {Kreitchmann}, R. and {Nielsen-Saines}, K. and {Kumwenda}, N. and {Joao}, E. and {Pinto}, J. and {Santos}, B. and {Parsons}, T. and {Kearney}, B. and {Emel}, L. and {Herron}, C.~M. and {Richardson}, P. and {Hudelson}, S.~E. and {Eshelman}, S.~H. and {George}, K. and {Fowler}, M.~G. and {Sato}, P. and {Mofenson} , L.},
title = "{Pharmacokinetics and safety of tenofovir in HIV-infected women during labor and their infants during the first week of life.}" ,
journal = {J. Acquir. Immune. Defic. Syndr.},
year = 2014,
volume = 65,
pages = {33-41},
}

@article{casey5,
author = {{Watts}, D.~H. and {Brown}, E.~R. and {Maldonado}, Y. and {Herron}, C.~M. and {Chipato}, T. and {Reddy}, L. and {Moodley}, D. and {Nakabiito}, C. and {Manji}, K. and {Fawzi}, W. and {George}, K. and {Richardson}, P. and {Zwerski}, S. and {Coovadia}, H. and {Fowler}, M.}, 
title = "{HIV disease progression in the first year after delivery among African women followed in the HPTN 046 clinical trial.}",
journal = {J. Acquir. Immune. Defic. Syndr.},
year = 2013,
volume = 64,
pages = {299-306},
}

@article{casey4,
author = {{Raymond}, V.~M. and {Herron}, C.~M. and {Giordano}, T.~J. and {Gruber}, S.~B.},
title = "{Familial renal cancer as an indicator of hereditary leiomyomatosis and renal cell cancer syndrome.}",
journal = {Fam. Cancer.},
year = 2012,
volume = 11,
pages = {115-121},
}

@article{casey3,
author = {{Marvin}, M.~L. and {Mazzoni}, S.~M. and {Herron}, C.~M. and {Edwards}, S. and {Gruber}, S.B. and {Petty}, E.~M.},
title = "{AXIN2-associated autosomal dominant ectodermal dysplasia and neoplastic syndrome.}",
journal = {Am. J. Med. Genet. A.},
year = 2011,
volume = 155,
pages = {898-902},
}

@article{casey2,
author = {{Rozek}, L.~S. and {Herron}, C.~M. and {Greenson}, J.~K. and {Moreno}, V. and {Capella}, G. and {Rennert}, G. and {Gruber}, S.~.B},
title =  "{Smoking, gender, and ethnicity predict somatic BRAF mutations in colorectal cancer.}",
journal = {Cancer Epidemiol. Biomarkers Prev.},
year = 2010,
volume = 19,
pages = {838-843},
}

@article{casey1,
author = {{Greenson}, J.~K. and {Huang}, S.~C. and {Herron}, C.~M. and {Moreno}, V. and {Bonner}, J.~D. and {Tomsho}, L.~P. and {Ben-Izhak}, O. and {Cohen}, H.~I. and {Trougouboff}, P. and {Bejhar}, J. and {Sova}, Y. and {Pinchev}, M. and {Rennert}, G. and {Gruber}, S.~B.},
title =  "{Pathologic predictors of microsatellite instability in colorectal cancer.}",
journal = {Am. J. Surg. Pathol.},
year = 2009,
volume = 33,
pages = {126-133},
}
\end{filecontents}

\bibliographystyle{aps-nameyear}      % American Physical Society (APS) style, author-year citations
\bibliography{herroncm}                % name your BibTeX data base
\nocite{*}

\end{resume}

\end{document}
